\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-04-20 journalWallFriction/experiment.tex
Edits to the paper and pictures.
Edited a lot of parts of the paper

The Intestine Phantom Model was used as the first test field of the project and was made to mimic an intestine and its villi. The model consists of a circular ring with an outer diameter of $50 mm$, an inner diameter of 46mm, and a thickness of 2mm created using a 3D printer and Fused filament fabrication. The model had some $2 mm$ long protrusions on its inner surface to mimic the effects of intestinal villi on the target particles.

@@

\begin{figure*}
\centering
\vspace{1.5em}
%\begin{overpic}[width=\columnwidth]{firstImage.jpg}\end{overpic}
\begin{overpic}[width=2\columnwidth]{3dexperiment.pdf}\end{overpic}
\caption{\label{fig:story}
Positioning particles that receive the same control inputs, but cannot move while a control input pushes them into a boundary.
} \vspace{-1em}
\end{figure*}

>>>>

The Intestine Phantom Model was used as the first test field of the project and was made to mimic an intestine and its villi. The model consists of a circular ring with an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and a thickness of 2mm created using a 3D printer and Fused filament fabrication. The model had some $2 mm$ long protrusions on its inner surface to mimic the effects of intestinal villi on the target particles. Fig.~\ref{fig:3dPrinted} shows an experiment with starting and ending positions drawn with marker on the workspace.

@@

\begin{figure*}\label{fig:3dPrinted}
\centering
\vspace{1.5em}
%\begin{overpic}[width=\columnwidth]{firstImage.jpg}\end{overpic}
\begin{overpic}[width=2\columnwidth]{3dexperiment.pdf}\end{overpic}
\caption{\label{fig:story}
Positioning particles that receive the same control inputs, but cannot move while a control input pushes them into a boundary.
} \vspace{-1em}
\end{figure*}

### 2018-04-20 journalWallFriction/simulation.tex
Updated the paper with new images, algorithms, edits, etc
Edits to the paper and pictures.
Edited a lot of parts of the paper

\subsection{Position Control of Two Robots}

Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using point robots (radius = $0$). 
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{numcontour.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{distcontour.pdf}\end{overpic}
\caption{\label{fig:contour}
Plots showing the algorithm with one goal on the boundary.
} \vspace{-1em}
\end{figure}

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{deltanum.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{deltadist.pdf}\end{overpic}
\caption{\label{fig:deltanumdist}
Plots showing decreasing error when the number of moves grows.
} \vspace{-1em}
\end{figure}

\begin{figure}
\centering
\renewcommand{\figwid}{1\columnwidth}
{\begin{overpic}[width =\figwid]{identical.png}
\end{overpic}
\begin{overpic}[width =\figwid]{contourDistnew.png}
\end{overpic}
\vspace{1em}
\begin{overpic}[width =\figwid]{JustSimulationV6.png}
%\put(97.5,21){5}
%\put(97.5,17.25){4}
%\put(97.5,13.5){3}
%\put(97.5,24){6}
%\put(97.5,27){7}
%\put(97.5,10){2}
%\put(97.5,7.5){1}
%\put(97.5,5){0}
\end{overpic}
}\caption{\label{fig:contourPlots}{Starting positions of robots $1$ and $2$ and goal position of robot $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The bottom row shows the number of moves required for the same configurations.}
\vspace{-1em}
}
\end{figure}

>>>>

%\subsection{Position Control of Two Robots}

Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. 
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{numcontour.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{distcontour.pdf}\end{overpic}
 \vspace{-2em}
\caption{\label{fig:contour}
Plots showing the algorithm with one goal on the boundary.
}
\end{figure}

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{deltanum.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{deltadist.pdf}\end{overpic}
\caption{\label{fig:deltanumdist}
Plots showing decreasing error as the number of moves grows.
} 
\vspace{-1em}
\end{figure}

\begin{figure}
\centering
\renewcommand{\figwid}{1\columnwidth}
{\begin{overpic}[width =\figwid]{identical.png}
\end{overpic}
\begin{overpic}[width =\figwid]{contourDistnew.png}
\end{overpic}
\vspace{1em}
\begin{overpic}[width =\figwid]{JustSimulationV6.png}
%\put(97.5,21){5}
%\put(97.5,17.25){4}
%\put(97.5,13.5){3}
%\put(97.5,24){6}
%\put(97.5,27){7}
%\put(97.5,10){2}
%\put(97.5,7.5){1}
%\put(97.5,5){0}
\end{overpic}
}\caption{\label{fig:contourPlots}{Starting positions of particles $1$ and $2$ and goal position of particle $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The bottom row shows the number of moves required for the same configurations.}
\vspace{-1em}
}
\end{figure}

### 2018-04-20 journalWallFriction/theory.tex
Edited a lot of parts of the paper

These system dynamics represent particle swarms in low-Reynolds number environments, where viscosity dominates inertial forces and so velocity is proportional to input force~\cite{Purcell1977}. 
 In this regime, the input force command $\mathbf{u}(t)$ controls the velocity of the robots.  
  The same model can be generalized to particles moved by fluid flow where the vector direction of fluid flow $\mathbf{u}(t)$ controls the velocity of particles, or for a swarm of robots that move at a constant speed in a direction specified by a uniform input $\mathbf{u}(t)$~\cite{Rubenstein2012}.
  As in our model, fluid flowing in a pipe has zero velocity along the boundary. Similar mechanical systems exist at larger scales, e.g. all tumblers of a combination look move uniformly unless obstructed by an obstacle.
 Our control problem is to design the control inputs $\mathbf{u}(t)$ to make all $n$ particles achieve a task.

 \subsection{Shortest Path in Square}\label{subsec:square}

 If the goal configuration can be reached in three moves, the first move makes one particle hit a wall, the second move adjusts the relative spacing error  to zero, and  the third move takes the particles to their final positions. 
The second move cannot be shortened, so optimization depends on choosing the location where the robot hits the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal hit location, as shown in Fig. \ref{fig:reflection}.

@@

 \subsection{Shortest Path in Unit Disk that Intersects Circumference}\label{subsec:circular}
 The shortest path between two points in the unit disk that reflects off the circumference is composed of two straight line segments shown in Fig.~\ref{fig:shortestpath}. The problem can be simplified by choosing the coordinate system carefully. We define the $x$ axis along the position of the starting point: $S=(s,0)$, and define the point of intersection by the angle $\theta$ from the $x$ axis $P=(\cos \theta,\sin \theta)$, and the final point $E$ by a radius $e$ and angle $\beta$, $E=e(\cos \beta,\sin \beta)$. Then the length of the two line segments is 
 \begin{equation}
\scriptsize{ \sqrt{(s-\cos \theta)^2+\sin^2 \theta}+\sqrt{(e \sin \beta-\cos \theta)^2+(e \sin \beta-\sin \theta)^2}},
 \end{equation}
 which is minimized by choosing an appropriate $\theta$ value. This equation can be simplified to

 \begin{equation}
 \sqrt{1+e^2-2 e \cos(\beta-\theta)}+\sqrt{1+s^2-2 s \cos \theta}. 
 \end{equation}

@@

 Simplifying this system of equations results in: $s=e \csc \theta (s \sin(2 \theta-\beta)+\sin(\beta-\theta))$. Solving this last equation results in a quartic solution that has a closed-form solution with four roots, each of which can be either a clockwise or a counterclockwise rotation $\theta$, depending on the sign of $\beta$, with $-\pi\leq\beta\leq\pi$. We evaluate each and select the solution that results in the shortest length path. This optimal path satisfies the law of reflection off the unit circle, with angle of incidence equal to angle of reflection. For an interactive mathematica demonstration of this shortest path, see \cite{shortestPathMathematica}.

>>>>

These system dynamics represent particle swarms in low-Reynolds number environments, where viscosity dominates inertial forces and so velocity is proportional to input force~\cite{Purcell1977}. 
 In this regime, the input force command $\mathbf{u}(t)$ controls the velocity of the particles.  
  The same model can be generalized to particles moved by fluid flow where the vector direction of fluid flow $\mathbf{u}(t)$ controls the velocity of particles, or for a swarm of particles that move at a constant speed in a direction specified by a uniform input $\mathbf{u}(t)$~\cite{Rubenstein2012}.
  As in our model, fluid flowing in a pipe has zero velocity along the boundary. Similar mechanical systems exist at larger scales, e.g. all tumblers of a combination look move uniformly unless obstructed by an obstacle.
 Our control problem is to design the control inputs $\mathbf{u}(t)$ to make all $n$ particles achieve a task.

 \subsection{Example: Shortest Path in a Square Workspace}\label{subsec:square}

 If the goal configuration can be reached in three moves, the shortest path has a simple solution. The first move makes one particle hit a wall, the second move adjusts the relative spacing error  to zero, and  the third move takes the particles to their final positions. 
The second move cannot be shortened, so optimization depends on choosing the location where the particle hits the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal hit location, as shown in Fig. \ref{fig:reflection}. There are four walls, and four candidate solutions.

@@

 \subsection{Shortest Path in Unit Disk that Intersects Circumference}\label{subsec:circular}
 The shortest path between two points in the unit disk that reflects off the circumference is composed of two straight line segments, as shown in Fig.~\ref{fig:shortestpath}. The problem can be simplified by choosing the coordinate system carefully. We define the $x$ axis along the position of the starting point: $S=(s,0)$, and define the point of intersection by the angle $\theta$ from the $x$ axis: $P=(\cos \theta,\sin \theta)$. Define the final point $E$ by a radius $e$ and angle $\beta$: $E=e(\cos \beta,\sin \beta)$. Then the length of the two line segments is 
 \begin{equation}
\scriptsize{ \sqrt{(s-\cos \theta)^2+\sin^2 \theta}+\sqrt{(e \sin \beta-\cos \theta)^2+(e \sin \beta-\sin \theta)^2}},
 \end{equation}
 which is minimized by choosing an appropriate $\theta$ value. This equation can be simplified to

 \begin{equation}
\sqrt{1+s^2-2 s \cos \theta}+  \sqrt{1+e^2-2 e \cos(\beta-\theta)}. 
 \end{equation}

@@

 Simplifying this system of equations results in $s=e \csc \theta (s \sin(2 \theta-\beta)+\sin(\beta-\theta))$. Solving this last equation results in a quartic solution that has a closed-form solution with four roots, each of which can be either a clockwise or a counterclockwise rotation $\theta$, depending on the sign of $\beta$, with $-\pi\leq\beta\leq\pi$. We evaluate each and select the solution that results in the shortest length path. This optimal path satisfies the law of reflection off the unit circle, with angle of incidence equal to angle of reflection. For an interactive Mathematica demonstration of this shortest path, see \cite{shortestPathMathematica}.
